Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.

### 2015-04-28 papers/MbhMsph/mm.tex
tuesday pill

\author{G. A. D. Savorgnan and A. W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}
\author{A. Marconi}
\affil{?}
\author{E. Sani}
\affil{European Southern Observatory, Alonso de Cordova, Vitacura 3107, Santiago, Chile.}
\and
\author{L.K. Hunt}
\affil{?}

@@

%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
%CTIO is operated by AURA, Inc.\ under contract to the National Science
%Foundation.}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

@@

\begin{abstract}
We present the latest scaling relations between black hole mass, $M_{\rm BH}$, 
and spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
which is minimally affected by dust and star formation. 
These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to investigate the poorly studied low-mass end of the correlations.
We provide updated linear regressions 
(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
indicating that gas-rich processes feed the black hole three times more efficiently than the host bulge. 
Disproving some previous claims, we also conclude that: 1) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
2) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.

@@

However, \cite{grahamscott2015} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
are not somehow randomly offset from the high-mass, near-linear correlation, 
but lie on the two times steeper relation traced by the S\'ersic spheroids. 
{\bf AL: would you like to add a sentence here, mentioning your forthcoming paper with ewan?} \\

@@

using state-of-the-art galaxy decompositions (Savorgnan \& Graham \emph{in preparation}, hereafter \emph{Paper I}) 

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. 
The inset displays, for all spheroids, the vertical offset 
from the correlation defined by spheroids with $n_{\rm sph} \geq 2$ only 
versus the spheroid S\'ersic index. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:pseudob}
\end{center}
\end{figure}

@@

\begin{table*}
\centering
\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & Kelly OLS$(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
                       & Kelly OLS$(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
                       & Kelly Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES OLS$(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & BCES OLS$(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
                       & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
                       & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]

Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\
                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
                   & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
                   & Kelly OLS$(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
                   & Kelly OLS$(X|Y)$  & $9.0 \pm 0.2$ & $-0.7 \pm 0.3$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
                   & Kelly Bisector    & $9.0 \pm 0.1$ & $-0.4 \pm 0.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]

S\'ersic (44) & BCES OLS$(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & BCES OLS$(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
              & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
              & Kelly OLS$(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
              & Kelly OLS$(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm 0.2$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
              & Kelly Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.1$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]

%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
%                      & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
%                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
%                      & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
%                      & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
%                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
%                      & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
%                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
%                      & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
%                      & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
%                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%
{\bf Early-type (E+S0)} (45) & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
                             & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
                             & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
                             & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
                             & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                             & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
                             & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
                             & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\
                             & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]

>>>>

\author{G. A. D. Savorgnan and A. W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}
\author{A. Marconi}
\affil{Dipartimento di Fisica e Astronomia, Universit\'a di Firenze, via G. Sansone 1, I-50019 Sesto Fiorentino, Firenze, Italy.}
\and
\author{E. Sani}
\affil{European Southern Observatory, Alonso de Cordova, Vitacura 3107, Santiago, Chile.}

@@

%\altaffiltext{1}{}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

@@

\begin{abstract}
We present the latest correlations of black hole mass, $M_{\rm BH}$, 
with spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
%which is minimally affected by dust and star formation. 
%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
and were derived from our state-of-the-art multicomponent galaxy decompositions 
that, for the first time, were checked to be consistent with the galaxy kinematics. 
Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to investigate the poorly studied low-mass end of the correlations.
%We provide updated linear regressions 
%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole from two to three times more efficiently than the host bulge. 
Disproving some previous claims, we also conclude that: i) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.

@@

However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
are not randomly offset from the high-mass, near-linear correlation, 
but follow the two times steeper relation traced by the S\'ersic spheroids. 
Using data from \cite{jiang2011a}, \cite{grahamscott2015} showed that this appears to extend to spheroids with even lower black hole masses 
($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\

@@

using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, \emph{in preparation}, hereafter \emph{Paper I}) 

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass versus $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
\label{fig:pseudob}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:pseudob}
\end{center}
\end{figure}

@@

\begin{table*}
\centering
\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY $(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & mFITEXY $(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES $(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & BCES $(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY $(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & mFITEXY $(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
                       & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
                       & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]

Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\
                   & BCES $(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY $(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
                   & mFITEXY $(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
                   & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
                   & {\tt linmix\_err} $(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
                   & {\tt linmix\_err} $(X|Y)$  & $9.0 \pm 0.2$ & $-0.7 \pm 0.3$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
                   & {\tt linmix\_err} Bisector    & $9.0 \pm 0.1$ & $-0.4 \pm 0.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]

S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & BCES $(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY $(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
              & mFITEXY $(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
              & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
              & {\tt linmix\_err} $(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm 0.2$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
              & {\tt linmix\_err} Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.1$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]

%Ellipticals (E) (30)   & BCES $(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
%                      & BCES $(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
%                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
%                      & FITEXY $(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
%                      & FITEXY $(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
%                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES $(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
%                      & BCES $(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
%                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
%                      & FITEXY $(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
%                      & FITEXY $(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
%                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%
{\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
                             & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
                             & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                             & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\
                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
